Development of a 3D display

### 2016-05-23 paper.tex
Formatting, bibliography

\documentclass[a4paper, 11pt, titlepage]{report}

\usepackage[margin=2.0cm]{geometry}

@@

@@

% Don't indent any first lines
\setlength{\parindent}{0mm}

% A little space between paragraphs
\setlength{\parskip}{1.5mm}

@@

As far as I know, however, only two people have built a working version of a three-dimensional
POV display so far (and have published it on the internet).\footnote{It turned out that there was
a third one: When I posted a picture of my project on the internet, a reddit user told me about
the display he built years before.}
Neither of these is being produced on a grand scale, instead they are --- like most 2D versions
--- side projects of hobbyists or engineers.

@@

Initially, all my images were made completely by hand. I had to enter the individual bits into the
program that would result in the desired image. Obviously this was a time-consuming and error
prone task. In order to simplify the process of making an image, I wrote a python program that
would support me in doing so. All of the source code is available on
\texttt{github.com/mbjd/\_3DPOV} in the folder \texttt{image\_creation}.

@@

>>>>

\documentclass[a4paper, 11pt, titlepage]{report}
\usepackage[margin=2.0cm]{geometry}

@@

% Load the "hyperref" package, and pass the hyphens option to the url package when it is loaded by
% hyperref. This allows urls to have \n's in them, with the correct link being clicable on both
% lines
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}

@@

\setlength{\parindent}{0mm} % Don't indent any first lines
\setlength{\parskip}{1.5mm} % A little space between paragraphs

@@

As far as I know, however, only two people have built a working version of a three-dimensional POV
display so far (and have published it on the internet).\footnote{It turned out that there was a
third one: When I posted a picture of my project on the internet, a reddit user told me about the
display he built years before.} Neither of these is being produced on a grand scale, instead they
are --- like most 2D versions --- side projects of hobbyists or engineers.
% todo - link or reference in footnote

@@

Initially, all my images were made completely by hand. I had to enter the individual bits into the
program that would result in the desired image. Obviously this was a time-consuming and error
prone task. In order to simplify the process of making an image, I wrote a python program that
would support me in doing so. All of the source code is available on
\url{https://github.com/mbjd/\_3DPOV} in the folder \texttt{image\_creation}.

@@

\section{Theoretical Limits}

The current version of the display works fine and well, but it's certainly not at the limit of
what can be done. In this section, I try to find out which aspects of the display can be improved
how much.

\subsection{Resolution}

The resolution was determined based upon the size of the LEDs I used. Pixels are located
\SI{3.125}{\milli\meter} apart from each other, while the LEDs themselves have a width of about
\SI{2.8}{\milli\meter}. In order to decrease pixel size significantly, I'd have to use smaller
pixels. To a certain extent, this would be possible; there are LEDs that are about half the width
of the ones I use currently.

With such small LEDs, there wouln't be enough space for the LED drivers. I didn't find chips with
similar functionality in a smaller package. To a certain extent it would be possible to minimise
the necessary space between LED drivers by using a multi-layer board layout. This method might
just be enough for twice the pixel density, but more won't be possible. Beyond that, custom-made
LED drivers are the only solution I can think of.

There's one more approach to increasing pixel density, which is to just have one colour per
pixel.

\begin{thebibliography}{99}

\bibitem{povdisp}
\emph{POV-Display}, project report, retrieved 2016-05-19,
\newline \url{http://www.mikrocontroller.net/articles/POV-Display}

\bibitem{attiny}
\emph{ATtiny85 POV Display}, build instructions by vishalapr, retrieved 2016-05-19
\newline \url{http://www.instructables.com/id/ATtiny8545-POV-Display/}

\bibitem{propclock}
\emph{Build an LED Propeller Clock}, build instructions by Bob Blick, retrieved 2016-05-19
\newline \url{http://www.jameco.com/Jameco/workshop/MyStory/diy-led-propeller-clock.html}

\bibitem{volumen}
\emph{voLumen - volumetric 3D display device}, project report by Maximilian Mali, 
retrieved 2016-05-19
\newline \url{https://hackaday.io/project/1737}

\bibitem{hotchkiss}
\emph{3D POV Display... Work in Progress}, video by Jason Hotchkiss, retrieved 2016-05-19
\newline \url{https://www.youtube.com/watch?v=rlptJzWwCXg}

\bibitem{povwiki}
\emph{Persistence of Vision} on Wikipedia, retrieved 2016-05-19
\newline \url{https://en.wikipedia.org/wiki/Persistence\_of\_vision}

% http://kiel.de/index.php?action=lexikon&tag=det&id=6114 would be here too but it's not availableanymore

\bibitem{teensy}
\emph{Teensy USB Development Board}, product page, retrieved 2016-05-19
\newline \url{https://www.pjrc.com/teensy/}

\bibitem{iiclib}
\emph{New \itwoc Library for Teensy 3}, forum post by nox771, retrieved 2016-05-19
\newline \url{https://forum.pjrc.com/threads/21680}

\bibitem{iictut}
\emph{\itwoc Tutorial}, article, retrieved 2016-05-19
\newline \url{http://www.best-microcontroller-projects.com/i2c-tutorial.html}

\bibitem{tlc}
\emph{TLC5927}, product page, retrieved 2016-05-19
\newline \url{http://www.ti.com/product/TLC5927}

\bibitem{tlcdigikey}
\emph{Texas-Instruments TLC5927IDBQR}, retrieved 2016-05-19
\newline \url{http://www.digikey.ch/product-detail/en/TLC5927IDBQR/296-24762-1-ND/}

\bibitem{eagle}
\emph{What is EAGLE}, product page, retrieved 2016-05-19
\newline \url{http://www.cadsoftusa.com/eagle-pcb-design-software/about-eagle/}

\bibitem{oshpark}
\emph{OSH Park --- An electric ecosystem}, retrieved 2016-05-19
\newline \url{https://oshpark.com/}

\bibitem{arduino}
\emph{Download the Arduino Software}, retrieved 2016-05-19
\newline \url{https://www.arduino.cc/en/main/software}

\bibitem{teensyduino}
\emph{Download Teensyduino}, retrieved 2016-05-19
\newline \url{https://www.pjrc.com/teensy/td\_download.html}

\bibitem{sublime}
\emph{Sublime Text 2}, product page, retrieved 2016-05-19
\newline \url{http://www.sublimetext.com/2}

\bibitem{stino}
\emph{Stino}, version control page by Robot-Will, retrieved 2016-05-19
\newline \url{https://github.com/Robot-Will/Stino}

\bibitem{intervaltimer}
\emph{IntervalTimer}, documentation page by Paul Stoffregen, retrieved 2016-05-19
\newline \url{https://www.pjrc.com/teensy/td\_timing\_IntervalTimer.html}

\bibitem{attachinterrupt}
\emph{attachInterrput()}, documentation page, retrieved 2016-05-19
\newline \url{https://www.arduino.cc/en/Reference/attachInterrupt}

\bibitem{kickstarter}
Comment by Paul Stoffregen, retrieved 2016-05-19
\newline
\url{https://www.kickstarter.com/projects/paulstoffregen/teensy-30-32-bit-arm-cortex-m4-usable-in-arduino-a/comments?cursor=1654857}

\bibitem{iopins}
\emph{Using Digital I/O Pins}, documentation page, retrieved 2016-05-19
\newline \url{https://www.pjrc.com/teensy/td\_digital.html}

\bibitem{spilib}
\emph{SPI Library}, documentation page, retrieved 2016-05-19
\newline \url{https://www.pjrc.com/teensy/td\_libs\_SPI.html}

\bibitem{pinout}
\emph{Teensy 3.1 Pins}, retrieved 2016-05-19
\newline \url{https://www.pjrc.com/teensy/pinout.html}

\bibitem{phoneplug}
\emph{Phone Connector (audio)} on Wikipedia, retrieved 2016-05-19
\newline \url{https://en.wikipedia.org/wiki/Phone\_connector}

\end{thebibliography}
